Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
updated paper again
added a table example

	\subsection{POS Bigram Model}
	POS Bigram Model (w/frequency count > 3)

@@

>>>>

	\subsection{POS Bigram Model}

	Table Example: 
    \begin{tabular} {l | c}
	 \hline
		Logical Formula & Program Type \\ \hline
		Implication & Function type $A \rightarrow B$\\ Proof of: & Function \\ \hline
		Conjunction & Pair type $A * B$ \\ Proof of: &  $(e_1, e_2)$ \\ \hline
		True & Unit \\ Proof of: &  $()$ \\ \hline
		False & Void \\ Proof of: & abort, failwith \\ \hline
		Disjunction & sumtype \\ Proof of: & tagged value \\ \hline
	 \end{tabular}

	POS Bigram Model (w/frequency count > 3)

@@

	Maybe could apply SVM to the (word sense: cosine-vector) approach (i.e. train an SVM 
	for every ambiguous word in the training data with the cosine vectors as input)
